%-------------------------
% Resume in Latex
% Author : Aaqil Raj Krishna
% Based off of: https://github.com/aaqilrk/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Aaqil Raj Krishna} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ \href{tel:919972522886}{\underline{+91 99725 22886}} ~ \href{mailto:aaqilrk@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{aaqilrk@gmail.com}} ~ 
    \href{https://aaqilrk.hashnode.dev/}{\raisebox{-0.2\height}\faGlobe\ \underline{aaqilrk.hashnode.dev}}  ~
    \href{https://www.linkedin.com/in/aaqil-krishna/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/aaqilrk}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} ~
     \href{https://leetcode.com/aaqilrk}{\raisebox{-0.2\height}\faCode\ \underline{LeetCode}} ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amrita School of Engineering}{Oct. 2020 -- May 2024}
      {Bachelor of Technology in Computer Science Engineering; \textbf{CGPA: 9.2/10.0}}{Bengaluru, India}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GirlScript Summer of Code}{May 2023 -- August 2023}
      {Open Source Contributor}{Remote}
      \resumeItemListStart
        \resumeItem{Chosen as an \textbf{Open Source Contributor} for the GirlScript Summer of Code 2023 initiative.}
        \resumeItem{Involved in diverse web-based projects, adeptly developing back-ends using \textbf{Express}, \textbf{orchestrating and facilitating project-related community meetings}, and \textbf{authoring comprehensive project documentation.}}
      \resumeItemListEnd
      \resumeSubheading
      {Ajiledone Technologies Pvt Ltd}{June 2022 -- August 2022}
      {Software Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Created a dynamic and responsive company website's front-end using \textbf{HTML, CSS, and JavaScript}, and deployed it on \textbf{DigitalOcean} for seamless access.}
        \resumeItem{Revitalized the client's website backend by refactoring and implementing new features with \textbf{Express.js and MongoDB}. Developed \textbf{RESTful APIs} to enable seamless communication with the front-end.}
        \resumeItem{Contributed to a \textbf{weather predictive model}, focused on forecasting detailed weather reports for the next 30 days, by conducting data preprocessing. Leveraged \textbf{data analysis} techniques to extract meaningful insights.}
        \resumeItem{Conducted statistical analysis of state-wise female education data using \textbf{NumPy and Pandas}, generating valuable insights to inform a government survey project.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Driving Behavior Classification} $|$ \emph{Python, NumPy, Pandas, Jupyter Notebook}}{\href{https://drive.google.com/file/d/1amb2g3hIKrMEGLnyRul-38z1Kxk2iqhz/view?usp=share_link}{\raisebox{-0.2\height}\ \underline{Paper}}}
          \resumeItemListStart
            \resumeItem{Classified drivers as normal or aggressive by applying machine learning algorithms to data generated by an \textbf{Android phone sensor}, making it useful for cab-sharing companies.}
            \resumeItem{Preprocessed the data using techniques such as normalization, feature selection, and balancing, using libraries like \textbf{NumPy and Pandas}.}
            \resumeItem{Created a classification model by implementing \textbf{logistic regression} with an \textbf{accuracy rate of 78\%}, providing valuable insights for the project stakeholders.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Online Bookstore} $|$ \emph{Node.js, Express.js, MySQL, Sequelize, Docker, EJS}}{\href{https://github.com/aaqilrk/pages}{\raisebox{-0.2\height}\ \underline{Github}}}
          \resumeItemListStart
            \resumeItem{Built a robust website that follows the \textbf{Model-View-Controller (MVC)} model, utilizing a \textbf{MySQL} database, \textbf{Node.js} server in the backend, and \textbf{EJS} for frontend rendering.}
            \resumeItem{Implemented a comprehensive authentication and authorization system that utilizes both \textbf{local and OAuth passport} implementations, along with cookies and sessions.}
            \resumeItem{Integrated \textbf{Sequelize} an ORM to establish a secure connection between the database and backend server, ensuring smooth data transactions.}
            \resumeItem{Implemented \textbf{Noty.js} for web push notifications, enhancing the user experience and providing real-time updates.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Donation Website} $|$ \emph{HTML, CSS, JavaScript}}{\href{https://github.com/aaqilrk/caritas}{\raisebox{-0.2\height}\ \underline{Github}}}
          \resumeItemListStart
            \resumeItem{Designed and developed an engaging frontend for a donation website using \textbf{HTML, CSS, and JavaScript}.}
            \resumeItem{Implemented a real-time map feature using \textbf{Google Maps API}, displaying donation centers and relevant information for easy access by users and deployed it using \textbf{GitHub Pages}.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, Scala, HTML/CSS, JavaScript} \\
     \textbf{Technologies/Frameworks}{: Linux, Git, Github Actions, Docker, Express.js, React, MySQL} \\
     \textbf{Developer Tools}{: VS Code, Jupyter Notebook, IntelliJ IDEA, Github} \\
     
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Co-curricular}
    % \resumeSubHeadingListStart
    %     \resumeSubheading{Fraternity}{}{}{}
    %         \resumeItemListStart
    %             \resumeItem{Achieved a 4 star fraternity ranking by the Office of Fraternity and Sorority Affairs (highest possible ranking).}
    %             \resumeItem{Managed executive board of 5 members and ran weekly meetings to oversee progress in essential parts of the chapter.}
    %             \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
    %         \resumeItemListEnd
        
    % \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeItemListStart
            \resumeItem{Published a series of informative \textbf{technical blogs} on diverse topics, such as Java architecture, Multithreading, Scala, and more, which can be accessed at \href{https://aaqilrk.hashnode.dev/}{\raisebox{-0.2\height}\faGlobe\ \textbf{\underline{aaqilrk.hashnode.dev}}}}
            \resumeItem{Participated in all-India hackathon organised by \textbf{GE Healthcare}, showcasing problem-solving and technical skills.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
